DraftOne

### 2016-07-24 writing/JSSDraft/JSSDraft.Rmd
Summarizing Bobb2015

>>>>

##High-dimensional problems

\citet{Bobb2015} used simulation to assess the performance of a proposed method for estimating the health effects of multi-pollutant exposures called Bayesian kernel machine regression (BKMR).  The authors generated exposure data by resampling from two representative data sets.  They then specified several different relationships between response and the components of each pollutant mixture to generate response data, for which they would need to use the customization features in eesim.  They fit kernel machine regression using both frequentist and Bayesian approaches, which would again require customization.  Their model performance measures included standard error of the estimates, power, and coverage, all of which eesim offers.  They found that there are advantages of using BKMR over KMR to detect relationships between mixture pollutants and health.
